Comparison with Christensen paper

### 2018-12-17 paper-comparison/compare-christensen.Rmd
Updated with 6 changepoint paper model
5 changepoints is still the lowest-deviance

<!-- skip for now due to error -->
<!-- ```{r LDATS changepoint} -->

<!-- ldats_cpt_paper_lda <- LDATS::TS_on_LDA(LDA_models = ldamodel, rodents[[2]], -->
<!--                                         formulas =c( '~ sin_year + cos_year'), nchangepoints = c(2, 3, 4, 5, 6)) -->

<!-- ``` -->

@@

save.image(file = '/Users/renatadiaz/Desktop/paper_cpt_ldats_lda.Rdata')

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))

@@

Running one with 6.

>>>>

```{r LDATS changepoint}

ldats_cpt_paper_lda <- LDATS::TS_on_LDA(LDA_models = ldamodel, rodents[[2]],
                                        formulas =c(~ sin_year + cos_year), nchangepoints = c(2, 3, 4, 5, 6))

@@

save.image(file = '/Users/renatadiaz/Desktop/paper_cpt_ldats_lda.Rdata') # saving it to the LDATS directory breaks git...?

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(6+1)+(6))

@@
